### 2024-02-07 README.Rmd
remove duplicate logos
resize logo

<img src="man/figures/logo.png" align="right" height="240"/>

@@

| function:               | purpose:                                                                                                                                   |
|------------|-----------------------------------------------|
| **st_bridges()**        | *Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.* |
| **st_quickmap_nb()**    | *Check contiguities visually on map.*                                                                                                      |
| **st_check_islands()**  | *Check assignment of island contiguities in a dataframe.*                                                                                  |
| **st_manual_join_nb()** | *Make manual changes to any connections.*                                                                                                  |
| **st_manual_cut_nb()**  | *Make manual changes to any connections.*                                                                                                  |

@@

| function:               | purpose:                                                 |
|-----------------|-------------------------------------------------------|
| **st_augment()**        | *Augment the original dataframe with model predictions.* |
| **st_quickmap_preds()** | *Generate quick maps of these predictions.*              |

@@

Further information and worked examples are available in this vignette.

>>>>

<!-- <img src="man/figures/logo.png" align="right" height="240"/> -->
<!-- # sfislands <a href="https://horankev.github.io/sfislands/"><img src="man/figures/logo.png" align="right" height="240" alt="sfislands website" /></a> -->

@@

| function:               | purpose:                                                                                                                                   |
|-----------------|-------------------------------------------------------|
| **st_bridges()**        | *Create a neighbours list, matrix, or `sf` dataframe containing a neighbours list or matrix as column "nb", while accounting for islands.* |
| **st_quickmap_nb()**    | *Check contiguities visually on map.*                                                                                                      |
| **st_check_islands()**  | *Check assignment of island contiguities in a dataframe.*                                                                                  |
| **st_manual_join_nb()** | *Make manual changes to any connections.*                                                                                                  |
| **st_manual_cut_nb()**  | *Make manual changes to any connections.*                                                                                                  |

@@

| function:               | purpose:                                                 |
|------------------|------------------------------------------------------|
| **st_augment()**        | *Augment the original dataframe with model predictions.* |
| **st_quickmap_preds()** | *Generate quick maps of these predictions.*              |

@@

Further information and worked examples are available in the vignettes which can be found [here](https://horankev.github.io/sfislands/).
